\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-21 icse/impl.tex
Revised Sec. 5

\paragraph{Intricate Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries require
labor-intensive manual modeling without adding any technical
contribution to this paper.  Thus, we decided not to support
four such libraries: \( \code{Math} \), \( \code{Date} \),
\( \code{RegExp} \), and \( \code{JSON} \).

>>>>

\paragraph{Orthogonal Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are orthogonal
to the JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support the four libraries.
